---
title: "Bio 316 HW 3"
output: html_document
date: "2024-06-17"
---

**Q1:** YAML stands for "yet another mark down language" and it is the specific syntax used to modulate the format of an R markdown document. It is one of three sections of an Rmd document. It defines the documents header information such as file output, title, author, and date.

**Q2:** If you set the code chunk option to include = false the code chunk, the code output, and the code message will not be in the finished file.  

**Q3:** Bee Data 

```{r, Q3a }
library(dplyr)
library(magrittr)
bee_df <- read.csv("bees.csv")
str(bee_df)
```
Structure: The data frame has 8 rows with 5 columns 

```{r, Q3b}
Bee_v1 <- dplyr::filter(.data = bee_df, year == 2016 | year == 2017 | year == 2018 | year == 2019 | year == 2020 | year == 2022 | year == 2023)
```

```{r, Q3c}
bee_v2 <- dplyr::select(.data = Bee_v1, -kleptoparasite_bees)
```

```{r, Q3d}
mutate(.data = bee_v2, total_bees = mason_bees + carpenter_bees + sweat_bees )
```
```{r, Q3e}
bee_v3p <- bee_df %>% 
dplyr::filter(year == 2016 | year == 2017 | year == 2018 | year == 2019 | year == 2020 |   year == 2022 | year == 2023) %>% 
  dplyr::select(-kleptoparasite_bees) %>% 
  mutate(total_bees = mason_bees + carpenter_bees + sweat_bees )
```
  
```{r, finstr}
str(bee_v3p)  
```  