---
title: "Burkhart_week 5 hw"
output: html_document
date: "2024-07-01"
---

## Question 1##
**Setup**
``` {r, Data Setup, warning = FALSE, message = FALSE}
library(palmerpenguins)
library(dplyr)
#Assigned penguin data to an object 
peng_df <- penguins

#Removed NA values 
pengv2_df <- dplyr::filter(.data = peng_df, sex == "male" | sex == "female")
```

**part a**
Answer: The best model to use would be the ANCOVA test because we have a categorical Y (flipper_length_mm) with 2 interacting continuous x (sex and species).

**part b**
``` {r, penguin ANCOVA}
# Set up ANCOVA
Ancova_test <- aov(flipper_length_mm ~ species + sex + species:sex, data = pengv2_df)

#Summary 
summary(Ancova_test)
```
**part c**
Answer: According to the summary table, sex and species are both significant in (p value <<< 0.005) and support the hypothesis that flipper length is in fact influenced by sex and species, however the interaction between sex and species is significant (p value = 0.00631) but not as significant as the variables alone. 

## Question 2##

**Part a**
``` {r, mmi}
#Created Models for MMI 
mod_1 <- aov(flipper_length_mm ~ sex * species + island, data = pengv2_df)
mod_2 <- aov(flipper_length_mm ~ species * sex * island, data = pengv2_df)
```

**part b**
``` {r, AIC}
#Ran AIC
AIC(mod_1,mod_2)
```
Answer: Model 1 had the lower AIC points but it wasn't a difference > 2 so both models are about equal in terms of fit. 

