---
title: "Burkhart wk 4 HW"
output: html_document
date: "2024-06-20"
---

**Question 1a**
``` {r,Tomato Data}
library(dplyr)
tom_df <- read.csv("tomato.csv")
tomtr_df <- df <- read.csv("tomato_treatment.csv")
tomi_df <- read.csv("tomato_issues.csv")
str(tom_df)
str(tomtr_df)
str(tomi_df)
```

**Question 1b**
``` {r,Tomato joining}
tomj_v1 <- left_join(x = tom_df, y = tomtr_df, by = "plant")
str(tomj_v1)
```
**Question 1c**
``` {r, Tomato filtering + join}
library(dplyr)
tomfj_v2 <- dplyr::filter(.data = tomi_df, problem == "none" | problem == "over watered"  )
tomfj_v3 <- left_join( x = tomfj_v2, y = tomj_v1)
str(tomfj_v3)
```

**Question 2a**
``` {r,Palmer Penguins}
library(palmerpenguins)
str(penguins)
```


**Question 2b**
``` {r,Penguins Data}
peng_df <- penguins
str(peng_df)
```
Column Name = __species__ Variable type = __Discrete__,
Column Name = __island__ Variable type = __Discrete__,
Column Name = __bill_length_mm__ Variable type = __Continuous__,
Column Name = __bill_depth_mm__ Variable type = __Continuous__,
Column Name = __flipper_length_mm__ Variable type = __Continuous__,
Column Name = __body_mass_g__ Variable type = __Continuous__ 
Column Name = __sex__ Variable type = __Discrete__,
Column Name __year__ Variable type = __Discrete__ 

**Question 2c**
```{r question_2c}
penga_df <- aov(flipper_length_mm ~ sex, data=peng_df)
summary(penga_df)
```
**Explanation** = The hypothesis that sex influences flipper length is statistically significant as the F value is very close to 0, This means we reject the null that sex doesn"t influence flipper length.


**Question 2d**
``` {r, Penguin stats v2}
pengr_df <- lm(body_mass_g ~ flipper_length_mm, data = peng_df)
summary(pengr_df)
```

**Explanation** = The hypothesis that higher body mass equates to longer flipper length is supported by the data with a very low p value of 2e -16 meaning the null is rejected. 