---
title: "Function Project: dndR"
output: html_document
date: "2024-06-18"
---

## Package Name: dndR##
``` {r, install dndR, message = FALSE, warning = FALSE}
library("dndR")
```





## **Function 1: roll**##
### Description:### 
The first function is called Roll. It is a function used to roll a specific die. The name of any given die is simply the letter "d" and the number of faces it possesses.

### Arguments:###

- Dice: Indicates which die and how many dice are being rolled. Arguments input must be the name and number of a die/dice i.e **_2d20_**

- Show_dice: An argument that allows each individual die's outcome in a group of dice rolled to be seen. The argument can be set as **_TRUE_** to show but its default input is **_FALSE_**  

- Re_roll: An argument that will re roll the dice if set to **_TRUE_** but defaults to **_FALSE_**

### Examples:###

_Example 1: Base function w/ default arguments_
``` {r, roll v1}
#Example
roll(dice = "4d10")
```

_Example 2: Function w/ show_dice = TRUE, shows the result of each die_
``` {r, roll v2}
#Example w/ show_dice = TRUE 
 roll(dice = "4d10", show_dice = TRUE)
```

_Example 3: Function w/ re_roll = TRUE, re rolls die_
``` {r,roll v3}
#Example w/ re_roll = TRUE 
roll(dice = "4d10", re_roll = TRUE)
```

_Example 4: Function w/ both arguments as = TRUE, re rolls dice and shows result of each die and total sum_
``` {r, roll v4}
#roll w/ both set to true 
roll(dice = "4d10", show_dice = TRUE, re_roll = TRUE)
```


## **Function 2: monster_creator**##
### Description:### 
Monster_creator is a function used to create a randomized data frame with two columns. The left column contains row names and the right is the numeric or character representing the row. 

### Arguments:### 

- Party_level: This argument indicates the numerical level of the dnd party. The argument's input is a **_numeric_**

- Party_size: This argument indicated the amount of people in a party. The input is also a **_numeric_**

``` {r, monster_creator}
#Example 
monster_creator(party_level = 12, party_size = 5)
```


## **Function 3: probability_plot**##
### Description:### 
This function creates a plot using **"ggplot2"** of real distributions of dice outcome possibilities.

### Arguments:###

- Dice: This argument indicates the name and number of the dice being rolled. The input is a **_character_**

- Roll_num: This argument indicates the amount of times the dice are rolled. The input is a **_numeric_**
``` {r, probability_plot}
#Example
probability_plot(dice = "d20", roll_num = 50)
``` 